First exclusive DVCS measurement off bound nucleon in $^4$He

### 2018-02-20 eg6-letters/incoherent/incoherent_prl.tex
update the abstract from stepan

%
\date{\today}
\begin{abstract}
We report on the beam-spin asymmetries associated with incoherent deeply 
   virtual Compton scattering off $^4$He in the valence quark region. The data 
   were accumulated using a 6 GeV longitudinally-polarized electron beam 
   incident on a pressurized $^4$He gaseous target placed in front of the CLAS 
   spectrometer in Hall-B at the Thomas Jefferson National Accelerator 
   Facility.  The baseline detection sub-systems of CLAS detected the scattered 
   electrons and the recoil protons, while the final-state real photons are 
   detected by a supplementary electromagnetic calorimeter at very forward 
   angles. The measured beam-spin asymmetries on bound-protons exhibit a 
   suppression compared to those on free proton, indicating possible medium 
   modifications on the nucleon's quark distributions and opening new 
   opportunities to explore the origin of the EMC effect within the framework 
   of the generalized parton distributions.

>>>>

%
\date{\today}
\begin{abstract}
%We report on the beam-spin asymmetries associated with incoherent deeply 
%virtual Compton scattering off $^4$He in the valence quark region. The data 
%were accumulated using a 6 GeV longitudinally-polarized electron beam incident 
%on a pressurized $^4$He gaseous target placed in front of the CLAS 
%spectrometer in Hall-B at the Thomas Jefferson National Accelerator Facility.  
%The baseline detection sub-systems of CLAS detected the scattered electrons 
%and the recoil protons, while the final-state real photons are detected by a 
%supplementary electromagnetic calorimeter at very forward angles. The measured 
%beam-spin asymmetries on bound-protons exhibit a suppression compared to those 
%on free proton, indicating possible medium modifications on the nucleon's 
%quark distributions and opening new opportunities to explore the origin of the 
%EMC effect within the framework of the generalized parton distributions.

 We report the first beam spin asymmetry (BSA) measurements in incoherent 
 deeply virtual Compton scattering (DVCS) off $^4$He using the fully exclusive 
 final state. The data were accumulated using a 6 GeV longitudinally polarized 
 electron beam incident on a pressurized $^4$He gaseous target placed in front 
 of the CLAS spectrometer in Hall-B at the Thomas Jefferson National 
 Accelerator Facility. The azimuthal angular ($\phi$) dependence of BSA is 
 studied in wide range of the virtual photon and the scattered proton 
 kinematics. The Q$^2$, $x_B$, and $t$ dependencies of BSA on bound nucleon has 
 been compared with one on free proton. In the whole kinematical region of our 
 measurements BSA on bound nucleon is by about $20\%$ to $30\%$ smaller, 
 indicating possible medium modification on the nucleon's partonic structure.  
 This measurement opens a new opportunity to explore the origin of the EMC 
 effect within the framework of the generalized parton distributions.
